---
title       : Weather Man
subtitle    : How the Weather Man works behind the scenes?
author      : Cem Demircioglu
job         : Consultant
framework   : io2012   # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

--- .class #id 

## Executive Summary


This presentation is about the Weather Man application that was designed by Cem Demircioglu. The application predicts the temperature of a selected date. The prediction is based on 10 years of data over a specific range of days. 


--- 

## Inner workings -- Data Acquisition

Pull the weather data from the internet and format it. 
```{r}
    #Get the data set from the URL 
    mydataframe <- read.fwf(
      file = url("http://academic.udayton.edu/kissock/http/Weather/gsod95-current/WASEATTL.txt"),
      widths=c(1,2, 7,9, 6,10, 5,9))
    
    #Create the report date by doing string concat. 
    mydataframe$ReportDate <- as.Date(
      paste(as.character(mydataframe[,2]),as.character(mydataframe[,4]),as.character(mydataframe[,6]),sep = "/")
      , "%m/%d/%Y")

#Pick the two columns from the dataframe
mydataframe <- mydataframe[,c(8,9)]
    
#Set the column names
colnames(mydataframe) <- c("Temp","ReportDate")


```

--- 

## Inner workings -- Data Acquisition

```{r}
    #User defined date parameter
    mydateend <- as.Date('2014-04-20')
    mynumberofdays <- 10
    
    #Define the final data frame
    myfinaldataframe <- data.frame(ReportDate=as.Date(character()),Temp=numeric()) 
    
    #Populate the final data frame
    for(i in 1:10) {
      
      tdate <- as.POSIXlt(mydateend)
      tdate$year <- tdate$year - i
      
      #Search for the dates 
      tempdf <- mydataframe[
        mydataframe[,2] > as.Date(tdate) - mynumberofdays & 
          mydataframe[,2] < as.Date(tdate)
        ,]
      
      #Add the rows to the new data frame
      myfinaldataframe <- rbind(myfinaldataframe,tempdf)
    }
    
```

--- 